% ════════════════════════════════════════════════════════════════════════════
% TÀI LIỆU THAM KHẢO
% ════════════════════════════════════════════════════════════════════════════
\chapter*{TÀI LIỆU THAM KHẢO}
\addcontentsline{toc}{chapter}{TÀI LIỆU THAM KHẢO}

\begin{enumerate}[label={[\arabic*]}]

  \item Flutter Documentation, Google (2024). \textit{Flutter --- Build apps for any screen}.\\
  \url{https://flutter.dev/docs}. Truy cập: 03/2025.

  \item Dart Programming Language, Google (2024). \textit{Dart --- The language behind Flutter}.\\
  \url{https://dart.dev/guides}. Truy cập: 03/2025.

  \item Firebase Documentation, Google (2024). \textit{Firebase --- App development platform}.\\
  \url{https://firebase.google.com/docs}. Truy cập: 03/2025.

  \item Cloud Firestore Data Model, Google (2024). \textit{Cloud Firestore Data model}.\\
  \url{https://firebase.google.com/docs/firestore/data-model}. Truy cập: 03/2025.

  \item Firebase Security Rules, Google (2024). \textit{Writing conditions for Cloud Firestore Security Rules}.\\
  \url{https://firebase.google.com/docs/firestore/security/rules-conditions}. Truy cập: 03/2025.

  \item Riverpod Documentation, Remi Rousselet (2024). \textit{Riverpod --- A Reactive Caching and Data-binding Framework}.\\
  \url{https://riverpod.dev/docs/introduction/why_riverpod}. Truy cập: 03/2025.

  \item Remi Rousselet (2024). \textit{Provider vs Riverpod: Understanding the differences}.\\
  \url{https://riverpod.dev/docs/from_provider/motivation}. Truy cập: 03/2025.

  \item Google AI for Developers (2024). \textit{Gemini API Documentation --- Quickstart}.\\
  \url{https://ai.google.dev/docs}. Truy cập: 03/2025.

  \item Material Design 3, Google (2024). \textit{Material Design Guidelines --- Color system}.\\
  \url{https://m3.material.io/styles/color/overview}. Truy cập: 03/2025.

  \item Flutter team (2024). \textit{State management approaches in Flutter}.\\
  \url{https://docs.flutter.dev/data-and-backend/state-mgmt/options}. Truy cập: 03/2025.

  \item fl\_chart package, Iman Khoshabi (2024). \textit{A highly customizable Flutter chart library}.\\
  \url{https://pub.dev/packages/fl_chart}. Truy cập: 03/2025.

  \item FlutterFire (2024). \textit{FlutterFire Overview --- Firebase for Flutter}.\\
  \url{https://firebase.flutter.dev/docs/overview}. Truy cập: 03/2025.

  \item SePay Documentation (2024). \textit{SePay --- Payment webhook API}.\\
  \url{https://sepay.vn/docs}. Truy cập: 04/2025.

  \item Supabase Documentation (2024). \textit{Supabase --- Open source Firebase alternative}.\\
  \url{https://supabase.com/docs}. Truy cập: 04/2025.

  \item Cloudflare Workers Documentation (2024). \textit{Cloudflare Workers --- Serverless execution environment}.\\
  \url{https://developers.cloudflare.com/workers/}. Truy cập: 04/2025.

  \item Felix Angelov (2024). \textit{BLoC Library --- A predictable state management library}.\\
  \url{https://bloclibrary.dev/}. Truy cập: 03/2025.

  \item Martin Fowler (2002). \textit{Patterns of Enterprise Application Architecture}. Addison-Wesley. Chapter: Repository Pattern.

  \item Robert C. Martin (2017). \textit{Clean Architecture: A Craftsman's Guide to Software Structure and Design}. Prentice Hall.

\end{enumerate}
